---
title: "R Programming Week 2: Assignment 1"
output: html_notebook
---


The function 'pollutantmean' calculates the mean of a pollutant (sulfate or nitrate) across a specified list of monitors. The function 'pollutantmean' takes three arguments: 'directory', 'pollutant', and 'id'. Given a vector monitor ID numbers, 'pollutantmean' reads that monitors' particulate matter data from the directory specified in the 'directory' argument and returns the mean of the pollutant across all of the monitors, ignoring any missing values coded as NA.
```{r}
pollutantmean <- function(directory, pollutant, id = 1:332)
{
  #create a list of files
  #the directory is the working directory we are in, the folder is "specdata"
  files_full <- list.files(directory, full.names = TRUE) 
  # create an empty data frame
  dat <- data.frame()
  for (i in id)
   {
       #add files to main data
       dat <- rbind(dat, read.csv(files_full[i]))
       
   }
    #Calulate mean
    mean_data <- mean(dat[, pollutant], na.rm = TRUE)
    return(mean_data)
}
```
The function 'complete' reads a directory full of files and reports the number of completely observed cases in each data file. The function should return a data frame where the first column is the name of the file and the second column is the number of complete cases. 
```{r}
complete <- function(directory, id = 1:332)
{
 #Create a list of file
 files_full <- list.files(directory, full.names= TRUE)
 # Create empty data frame 
 dat <- data.frame()
 for (i in id)
 {
   # Read files
   temp <- read.csv(files_full[i])
   # nobs are sum of all complete cases
   nobs <-sum(complete.cases(temp))
   # Enamurtates complete cass by index
   dat <-rbind(dat, data.frame(i, nobs))
   
}
  colnames(dat) <- c("id", "nobs")
  return(dat)
}
```
The function 'corr' takes a directory of data files and a threshold for complete cases and calculates the correlation between sulfate and nitrate for monitor locations where the number of completely observed cases (on all variables) is greater than the threshold. The function should return a vector of correlations for the monitors that meet the threshold requirement. If no monitors meet the threshold requirement, then the function should return a numeric vector of length 0.
```{r}
corr <- function(directory, threshold = 0)
{
 #create list of all files
  files_full <- list.files(directory, full.names= TRUE)
 # create empty data set
  dat <- vector(mode = "numeric", length = 0)
  for(i in 1:length(files_full))
  {
      # Read File
       tmp <- read.csv(files_full[i])
   
       #Calculate csum    
       csum <- sum((!is.na(tmp$sulfate)) & (!is.na(tmp$nitrate)))
      if (csum > threshold)
      {
        #Extract data of niteate and sulfate and calculate correlation between them
         sul <- tmp[which(!is.na(tmp$sulfate)), ]
         nit <- sul[which(!is.na(sul$nitrate)), ]
         dat <- c(dat, cor(nit$sulfate, nit$nitrate))
      }
  }
   
    dat
}
```
##Quiz
Q1. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.
```{r}
pollutantmean("specdata", "sulfate", 1:10)
```
Q2. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.
```{r}
pollutantmean("specdata", "nitrate", 70:72)
```
Q3. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.
```{r}
pollutantmean("specdata", "sulfate", 34)
```
Q4. What value is returned by the following call to pollutantmean()? You should round your output to 3 digits.
```{r}
pollutantmean("specdata", "nitrate")
```
Q5. What value is printed at end of the following code?
```{r}
cc <- complete("specdata", c(6, 10, 20, 34, 100, 200, 310))
print(cc$nobs)
```
Q6. What value is printed at end of the following code?
```{r}
cc <- complete("specdata", 54)
print(cc$nobs)
```
Q7. What value is printed at end of the following code?
```{r}
set.seed(42)
cc <- complete("specdata", 332:1)
use <- sample(332, 10)
print(cc[use, "nobs"])
```
Q8. What value is printed at end of the following code?
```{r}
cr <- corr("specdata")                
cr <- sort(cr)                
set.seed(868)                
out <- round(cr[sample(length(cr), 5)], 4)
print(out)
```
Q9. What value is printed at end of the following code?
```{r}
cr <- corr("specdata", 129)                
cr <- sort(cr)                
n <- length(cr)                
set.seed(197)                
out <- c(n, round(cr[sample(n, 5)], 4))
print(out)
```
Q10. What value is printed at end of the following code?
```{r}
cr <- corr("specdata", 2000)                
n <- length(cr)                
cr <- corr("specdata", 1000)                
cr <- sort(cr)
print(c(n, round(cr, 4)))
```
